Offline Reinforcement Learning with In-Sample Tsallis Regularized Policy

### 2023-05-04 paper/main.tex
updated the paper a bit

% to compile a preprint version, e.g., for submission to arXiv, add add the
% [preprint] option:
\usepackage[preprint]{nips_2018}

@@

We focus on discrete-time discounted Markov Decision Processes (MDPs) expressed by the tuple $(\mathcal{S}, \mathcal{A}, P,  r,  \gamma)$, where $\mathcal{S}$ and $\mathcal{A}$ denote state space and finite action space, respectively. 
% $d(\cdot)$ denotes the initial state distribution.
$P(\cdot |s,a)$ denotes transition probability over the state space given state-action pair $(s,a)$,  
and $r(s,a)$ defines the reward associated with that transition. 
$\gamma \in (0,1)$ is the discount factor.
A policy $\pi(\cdot|s)$ is a mapping from the state space to distributions over actions.
% The stationary state distribution induced by $\pi$ can then be defined as $d^{\pi}_{\mu}(s)\!:=\!(1-\gamma)\sum^{\infty}_{t=0}\gamma^{t}P(s_t=s|\pi, \mu)$.
% We define the state value function at a specific state $s$ following policy $\pi$  as  $V_{\pi}(s) = \mathbb{E}\AdaRectBracket{\sum_{t=0}^{\infty} r_t | s }$.
The state-action value function starting from $(s, a)$ following policy $\pi$ is defined as  $Q_{\pi}(s,a) = \mathbb{E}_{\pi}\AdaRectBracket{\sum_{t=0}^{\infty} \gamma^t r(s_t, a_t) | s_0=s, a_0 = a }$.
It is a classic result that there exists a stationary optimal policy that maximizes the cumulative return \cite{Puterman1994}.
Its fixed point $Q_{*}(s,a)$ satisfies the Bellman optimality equation $Q_{*}(s,a) = r(s,a) + \gamma  \mathbb{E}_{s'\sim P(\cdot|s,a)}\!\AdaRectBracket{\max_{a'}Q_*(s',a')}$.
Therefore, in practice it is common to update the action value function by acting greedily with respect to the current estimate.

@@

\begin{figure}
    \centering
    \begin{subfigure}[b]{0.3\textwidth}
        \includegraphics[width=\textwidth]{img/q_stat_illus.png}
    \end{subfigure}
    \begin{subfigure}[b]{0.3\textwidth}
        \includegraphics[width=\textwidth]{img/tsallis_entropy.png}
    \end{subfigure}
    \begin{subfigure}[b]{0.3\textwidth}
        \includegraphics[width=\textwidth]{img/tsallis_kl.png}
    \end{subfigure}
    \caption{(Left) Behavior of \qlog and $q$-exponential functions.
    When $q=1$ they respectively recover the standard logarithm and exponential.
    (Mid) Tsallis entropy of the Gaussian policy $\mathcal{N}(2, 1)$. (Right) Tsallis KL divergence between two Gaussian policies $\mathcal{N}(2.75, 1)$ and $\mathcal{N}(3.25, 1)$.
    }
    \label{fig:q_stats}
\end{figure}

In this paper we consider a broad class of less studied entropic regularizer known as the Tsallis entropy $S_q(\pi(\cdot|s)):= \frac{1}{q-1} \AdaBracket{\sum_a \pi^q(a|s) - 1}$, where $q \in \mathbb{R}_{+}$.
It is also called generalized entropy since it generalizes the Shannon entropy \cite{TsallisEntropy,tsallis2009introduction}.
Tsallis entropy can also be defined by the \qlog in a similar manner to the standard logarithm defining Shannon entropy, hence eases the notation and derivation.
\qlog and its unique inverse function $q$-exponential are defined by \cite{tsallis2009introduction}:
\begin{align}
    \begin{split}
        \logq{x} = \frac{x^{q-1} - 1}{q-1}, \quad \expq{x} = \AdaRectBracket{1 + (q - 1)x}^{\frac{1}{q-1}}_{+}, \quad \tsallis{\pi(\cdot|s)} = -\sum_{a}{\pi(a|s)}{\logq{\pi(a|s)}},
    \end{split}
\end{align}
where $[\cdot]_{+} = \max \{\cdot, 0\}$.
When $q\rightarrow 1$, the \qlog (resp. $q$-exponential) recovers the standard logarithm (resp. exponential) and hence Tsallis entropy degenerates to Shannon entropy.
When $q=2$, we arrive at the Tsallis sparse entropy 
$S_2(\pi(\cdot | s)):= \pi(a|s)\AdaBracket{1 - \pi(a|s)}$ \cite{Nachum18a-tsallis,Lee2018-TsallisRAL}. 
The name sparse entropy comes from the fact that the regularizer leads to sparse support for the resulting policy \cite{Blondel-2020LearningFenchelYoundLoss,Martins16-sparsemax}.
When $q=\infty$, the regularizer vanishes.
In Figure \ref{fig:q_stats} we plot the behavior of $q$-statistics under different $q$.

We can write out the regularized policy for general Tsallis entropy regularization for any $q$\footnotemark\footnotetext{Different to prior works \cite{Lee2018-TsallisRAL,Nachum18a-tsallis}, our definition of $\psi$ has an additional $\frac{1}{q-1}$ term to accommodate the $q$-exponential policy, see Appendix \ref{apdx:derivation} for derivation.}:
\begin{align}
    \pi(a|s) = \exp_q \AdaBracket{\frac{Q(s,a)}{\tau } - {\psi}\AdaBracket{\frac{Q(s, \cdot)}{\tau }}}, \,\,
    {\psi}\AdaBracket{\frac{Q(s,\cdot)}{\tau}} \doteq \frac{\sum_{a\in K(s)} \frac{Q(s,a)}{\tau} - 1 }{|K{(s)}|} + \frac{1}{q-1}.
    \label{eq:tsallis_policy}
\end{align}
  $K(s)$ is the set of highest-value actions satisfying $1 \!+\! i\frac{Q(s,a_{(i)})}{\tau} \!>\! \sum_{j=1}^{i}\frac{Q(s,a_{(j)})}{\tau}$, with $a_{(j)}$ denotes the $j$-th largest action.
  Intuitively, the policy first sorts actions by $a_{(1)}, \dots, a_{(|\mathcal{A}|)}$ and then compute the threshold $\psi$.
  Suppose $Q(s, a_{(j+1)}) \leq \psi \leq Q(s, a_{(j)})$, then actions from $a_{(j+1)}, \dots, a_{(|\mathcal{A}|)}$ are truncated and have zero probability of being selected.
  The truncation effect can be controlled by $\tau$.

  Note that for $q\neq 1,2,\infty$ the policy does not have a closed-form solution. 
  Nonetheless we can resort to the Taylor's expansion to obtain an approximate policy, see Appendix \ref{apdx:derivation} for details. 
  For those cases \eq{\ref{eq:tsallis_policy}} still holds, but may need an additional renormalization step to guarantee a valid probability distribution. 
  Therefore, in the rest of the paper, we write $\pi(a|s) \propto \exp_q\AdaBracket{\frac{Q(s,a)}{\tau}}$.
  The effect of $q$ lies in defining the range of the acceptable actions in $K(s)$ or extent of action truncation. 
  Indeed, we can show that as $q \rightarrow \infty$, the unnormalized Taylor's expansion for the policy $\pi(a|s) \rightarrow 1, \, \forall a$, that is, after normalization it becomes a uniform distribution.
We plot the behavior of action truncation in Figure \ref{fig:q_truncation} for two commonly used policy classes, and indeed as $q$ gets larger the truncation becomes weaker.
% \begin{figure}
%     \centering
%     \begin{subfigure}[b]{0.49\textwidth}
%         \centering
%         \includegraphics[width=\textwidth]{img/tsallis_entropy.png}
%         \label{fig:y equals x}
%     \end{subfigure}
%     \hfill
%     \begin{subfigure}[b]{0.49\textwidth}
%         \centering
%         \includegraphics[width=\textwidth]{img/tsallis_kl.png}
%         \label{fig:three sin x}
%     \end{subfigure}
%     \caption{Estimation of policy ratio $\frac{\pi_{k+1}}{\pi_k}$ during learning of Munchausen DQN on \texttt{CartPole-v1} and \texttt{LunarLander-v2}.
%     Notice the $y$-axis is at the magnitude of $10^{35}$.
%     }
%     \label{fig:mdqn_policy_ratio}
% \end{figure}

Very recently \citet{zhu2023generalized} proposed in RL to exploit Tsallis KL divergence which generalizes Tsallis entropy.  
They proved that the regularized optimal policy takes a similar form to the optimal KL-regularized policy:
% Recall that, this definition is different from the statistical physics definition \citep{Furuichi2004-fundamentals-qKL}:
\begin{align}
    \begin{split}
        \qKLany{\pi(\cdot|s)}{\mu(\cdot|s)} = \sum_a \pi(a|s) \ln_{q} \frac{\pi(a|s)}{\mu(a|s)}, \quad \pi(a|s) = \mu(a|s) \exp_q\AdaBracket{\frac{Q_{\pi}(s,a)}{\tau} - \psi\AdaBracket{\frac{Q_{\pi}(s,a)}{\tau}} }.
    \end{split}
    \label{eq:tkl_policy}
\end{align}
We can also resort to Taylor's expansion and renormalization to obtain approximate policies, hence the policy can be written as $\pi(a|s)\propto \mu(a|s)\exp_q\AdaBracket{\frac{Q_{\pi}(s,a)}{\tau}}$.
It is worth noting that unlike the KL divergence, the Tsallis KL divergence cannot be decomposed as $\ln_q\!\frac{\pi(a|s)}{\mu(a|s)} \neq \ln_q \pi(a|s) - \ln_q \mu(a|s)$.
% \eq{\ref{eq:tkl_policy}} is important to our application of offline RL where we show the in-sample softmax becomes in-sample sparsemax.

\begin{figure}[t]
    \centering
    \begin{subfigure}[b]{0.245\textwidth}
        \includegraphics[width=\textwidth]{img/q2_Gaussian_sparsemax.png}
    \end{subfigure}
    \begin{subfigure}[b]{0.245\textwidth}
        \includegraphics[width=\textwidth]{img/q50_scaled_Gaussian_sparsemax.png}
    \end{subfigure}
    \begin{subfigure}[b]{0.245\textwidth}
        \includegraphics[width=\textwidth]{img/q2.0_Boltzmann_sparsemax.png}
    \end{subfigure}
    \begin{subfigure}[b]{0.245\textwidth}
        \includegraphics[width=\textwidth]{img/q50_Boltzmann_sparsemax.png}
    \end{subfigure}
    \caption{
        The sparsemax operator acting upon Gaussian and Boltzmann policies for $q=2$ and $q=50$ by truncating actions with values lower than $\psi$. 
    As $q\rightarrow \infty$ the policy tends toward uniform distribution.
    We assume the The dataset is generated by Tsallis policies such that the actions absent from the offline dataset are those being truncated.
    }
    \label{fig:q_truncation}
\end{figure}

@@

More importantly, the support constraint is naturally satisfied since 
the learned Tsallis policy learns a new set of allowable actions $K_{t, q}$ from $K_\mathcal{D}(s)$ depending on $q$ and iteration $t$.
The set satisfies the condition $K_{t, q} \preceq K_\mathcal{D}$:
 i.e. $|K_{t, q}| \leq |K_\mathcal{D}|$ and support constraint $\pi_t \preceq \datasetPolicy$.
 Let us take $q=2$ for example:
 \begin{align}
    \begin{split}
    &Q_{t+1, \datasetPolicy}(s,a) = r(s,a) +  \gamma \expectation{s'\sim P(\cdot | s,a)}{ \sum_{a' \in K_{\mathcal{D}}(s)} \!\!\!\!\! \pi_{t+1}(a'|s') \AdaBracket{Q_{t, \datasetPolicy}(s',a') - \tau S_2(\pi_{t+1}(\cdot|s'))}}\\
    &\qquad = r(s,a) + \gamma \expectation{s'\sim P(\cdot | s,a)}{ \tau\sum_{a' \in K_{\mathcal{D}}(s)} \!\! \AdaBracket{\frac{Q_{t, \datasetPolicy}(s',a')}{\tau}}^2 - \AdaBracket{ \psi\AdaBracket{\frac{Q_{t, \datasetPolicy}(s',a')}{\tau}} - 1 }^2 + \tau}\\
    &\qquad = r(s,a) + \gamma \expectation{s'\sim P(\cdot | s,a)}{ \tau\sum_{a' \in K_{t,q}(s)} \!\! \AdaBracket{\frac{Q_{t, \datasetPolicy}(s',a')}{\tau}}^2 - \AdaBracket{ \psi\AdaBracket{\frac{Q_{t, \datasetPolicy}(s',a')}{\tau}} - 1 }^2 + \tau}.
    \end{split}
    \label{eq:tsallis_backward_q2}
 \end{align}
 The second equation is because $\max_{\pi}\sum_{a\in\pi(\cdot|s)}\pi(a|s)Q(s,a) - \tau S_2(\pi(\cdot|s))$ attains its maximum at $\tau \sum_{a \in K(s)}\AdaBracket{ \frac{Q(s,a)}{\tau} }^2 - \psi\AdaBracket{\frac{Q(s, \cdot)}{\tau}}^2 + \tau$ \cite{Lee2018-TsallisRAL,Martins16-sparsemax}, and the last equation is due to $K_{t, q} \preceq K_\mathcal{D}$.
 \eq{\ref{eq:tsallis_backward_q2}} states that, one needs not to explicitly enforce the support constraint since it is automatically fulfilled by learning a new subset of allowable actions.
% That is, the backward Bellman optimality equation becomes:
% \begin{align}
%     \begin{split}
%         \datasetOptimalQ(s,a) &= r(s,a) +  \gamma \expectation{s'\sim P(\cdot | s,a)}{ \sum_{a' \in K_\mathcal{D}(s')} \pi_{*, \datasetPolicy}(a'|s') \AdaBracket{\datasetOptimalQ(s',a') - \tau S_2(\pi_{*, \datasetPolicy})(\cdot|s')}}. 
%     \end{split}
% \end{align}
% The term inside the expectation is now:
% \begin{align}
%     \begin{split}
%         & \sum_{a' \in K_\mathcal{D}(s')} \pi_{*, \datasetPolicy}(a'|s') \AdaBracket{\datasetOptimalQ(s',a') - \tau S_2(\pi_{*, \datasetPolicy})(\cdot|s')} \\ 
%          &= \sum_{a' \in K_\mathcal{D}(s')} \pi_{*, \datasetPolicy}(a'|s') \AdaBracket{ \datasetOptimalQ(s',a') + \frac{\tau}{2}(1 - \pi_{*, \datasetPolicy}(a'|s')) } \\
%          &= \sum_{a' \in K_\mathcal{D}(s')} \pi_{*, \datasetPolicy}(a'|s') \AdaBracket{ \datasetOptimalQ(s',a') - \frac{\tau}{2}\pi_{*, \datasetPolicy}(a'|s') } + \frac{\tau}{2} \\
%          &= \sum_{a' \in K_\mathcal{D}(s')} \frac{\AdaRectBracket{ \tau^{-1}Q_{t, \datasetPolicy}(s,a)}_+ }{\sum_{b\in K_\mathcal{D}(s')}\tau^{-1} Q_{t, \datasetPolicy}(s,b)}
%     \end{split}
% \end{align}

>>>>

% to compile a preprint version, e.g., for submission to arXiv, add add the
% [preprint] option:
\usepackage{nips2023}

@@

RL problems are usually modelled by Markov Decision Processes (MDPs) expressed by the tuple $(\mathcal{S}, \mathcal{A}, P,  r,  \gamma)$, where $\mathcal{S}$ and $\mathcal{A}$ respectively denote state space and action space. 
% $d(\cdot)$ denotes the initial state distribution.
$P(\cdot |s,a)$ denotes transition probability over the state space given state-action pair $(s,a)$,  
and $r(s,a)$ defines the reward associated with that transition. 
$\gamma \in (0,1)$ is the discount factor.
A policy $\pi(\cdot|s)$ is a mapping from the state space to distributions over actions.
% The stationary state distribution induced by $\pi$ can then be defined as $d^{\pi}_{\mu}(s)\!:=\!(1-\gamma)\sum^{\infty}_{t=0}\gamma^{t}P(s_t=s|\pi, \mu)$.
% We define the state value function at a specific state $s$ following policy $\pi$  as  $V_{\pi}(s) = \mathbb{E}\AdaRectBracket{\sum_{t=0}^{\infty} r_t | s }$.
The state-action value function starting from $(s, a)$ following policy $\pi$ is defined as  $Q_{\pi}(s,a) = \mathbb{E}_{\pi}\AdaRectBracket{\sum_{t=0}^{\infty} \gamma^t r(s_t, a_t) | s_0=s, a_0 = a }$.
It is a classic result that there exists a stationary optimal policy that maximizes the cumulative return \cite{Puterman1994}.
Its fixed point $Q_{*}(s,a)$ satisfies the Bellman optimality equation $Q_{*}(s,a) = r(s,a) + \gamma  \mathbb{E}_{s'\sim P(\cdot|s,a)}\!\AdaRectBracket{\max_{a'}Q_*(s',a')}$.
Therefore, in practice it is common to update the action value function by acting greedily with respect to the current estimate.

@@

% \begin{figure}
%     \centering
%     \includegraphics[width=0.33\textwidth]{img/Gaussian_ks.png}
%     \caption{xs}
% \end{figure}
% \begin{figure}
%     \centering
%     \begin{subfigure}[b]{0.3\textwidth}
%         \includegraphics[width=\textwidth]{img/q_stat_illus.png}
%     \end{subfigure}
%     \begin{subfigure}[b]{0.3\textwidth}
%         \includegraphics[width=\textwidth]{img/tsallis_entropy.png}
%     \end{subfigure}
%     \begin{subfigure}[b]{0.3\textwidth}
%         \includegraphics[width=\textwidth]{img/tsallis_kl.png}
%     \end{subfigure}
%     \caption{(Left) Behavior of \qlog and $q$-exponential functions.
%     When $q=1$ they respectively recover the standard logarithm and exponential.
%     (Mid) Tsallis entropy of the Gaussian policy $\mathcal{N}(2, 1)$. (Right) Tsallis KL divergence between two Gaussian policies $\mathcal{N}(2.75, 1)$ and $\mathcal{N}(3.25, 1)$.
%     }
%     \label{fig:q_stats}
% \end{figure}

In this paper we consider a broad class of less studied entropic regularizer known as the Tsallis entropy $S_q(\pi(\cdot|s)):= \frac{1}{q-1} \AdaBracket{1-\sum_a \pi^q(a|s)}$, where $q \in \mathbb{R}_{+}$.
It is also called generalized entropy since it generalizes the Shannon entropy \cite{TsallisEntropy,tsallis2009introduction}.
Tsallis entropy can also be defined by the \qlog in a similar manner to the standard logarithm defining Shannon entropy, hence eases the notation and derivation.
\qlog and its unique inverse function $q$-exponential are defined by \cite{tsallis2009introduction}:
\begin{align}
    \begin{split}
        \logq{x} = \frac{x^{q-1} - 1}{q-1}, \quad \expq{x} = \AdaRectBracket{1 + (q - 1)x}^{\frac{1}{q-1}}_{+}, \quad \tsallis{\pi(\cdot|s)} = -\sum_{a}{\pi(a|s)}{\logq{\pi(a|s)}},
    \end{split}
\end{align}
where $[\cdot]_{+} = \max \{\cdot, 0\}$.
When $q\rightarrow 1$, the \qlog (resp. $q$-exponential) recovers the standard logarithm (resp. exponential) and hence Tsallis entropy degenerates to Shannon entropy.
When $q=2$, we arrive at the Tsallis sparse entropy 
$S_2(\pi(\cdot | s)):= \pi(a|s)\AdaBracket{1 - \pi(a|s)}$ \cite{Nachum18a-tsallis,Lee2018-TsallisRAL}. 
The name sparse entropy comes from the fact that the regularizer leads to sparse support for the resulting \emph{sparsemax} policy \cite{Blondel-2020LearningFenchelYoundLoss,Martins16-sparsemax}.
When $q=\infty$, the regularizer vanishes.
% In Figure \ref{fig:q_stats} we plot the behavior of $q$-statistics under different $q$.
In this paper, we call the regularized policy sparsemax for all $q$ , and express them using the $q$-exponential\footnotemark\footnotetext{Different to prior works \cite{Lee2018-TsallisRAL,Nachum18a-tsallis}, our definition of $\psi$ has an additional $\frac{1}{q-1}$ term to accommodate the $q$-exponential policy, see Appendix \ref{apdx:derivation} for derivation.}:
\begin{align}
    \pi(a|s) = \exp_q \AdaBracket{\frac{Q(s,a)}{\tau } - {\psi}\AdaBracket{\frac{Q(s, \cdot)}{\tau }}}, \,\,
    {\psi}\AdaBracket{\frac{Q(s,\cdot)}{\tau}} \doteq \frac{\sum_{a\in K(s)} \frac{Q(s,a)}{\tau} - 1 }{|K{(s)}|} + \frac{1}{q-1}.
    \label{eq:tsallis_policy}
\end{align}
  $K(s)$ is the set of highest-value actions satisfying $1 \!+\! i\frac{Q(s,a_{(i)})}{\tau} \!>\! \sum_{j=1}^{i}\frac{Q(s,a_{(j)})}{\tau}$, with $a_{(j)}$ denotes the $j$-th largest action.
  Intuitively, the policy first sorts actions by $a_{(1)}, \dots, a_{(|\mathcal{A}|)}$ and then compute the threshold $\psi$.
  Suppose $Q(s, a_{(j+1)}) \leq \psi \leq Q(s, a_{(j)})$, then actions from $a_{(j+1)}, \dots, a_{(|\mathcal{A}|)}$ are truncated and have zero probability of being selected.
  The actions $a_{(1)}, \dots, a_{(j)}$ are called allowable actions and collected in the set $K(s)$.
  The degree of truncation and the size of $K(s)$ can be controlled by $\tau$. The truncation is visualized in Figure \ref{fig:simplex_truncate}.

  Note that for $q\neq 1,2,\infty$ the policy does not have a closed-form solution. 
  Nonetheless we can resort to the Taylor's expansion to obtain approximate sparsemax policies, see Appendix \ref{apdx:derivation} for details. 
  For those cases \eq{\ref{eq:tsallis_policy}} still holds, but may need an additional renormalization step to guarantee a valid probability distribution. 
  Therefore, in the rest of the paper, we write $\pi(a|s) \propto \exp_q\AdaBracket{\frac{Q(s,a)}{\tau}}$.
  The effect of $q$ lies in defining the range of the acceptable actions in $K(s)$ or extent of action truncation. 
  Indeed, we can show that as $q \rightarrow \infty$, the unnormalized Taylor's expansion for the policy $\pi(a|s) \rightarrow 1, \, \forall a$, that is, after normalization it becomes a uniform distribution.
  We compare argmax, softmax, sparsemax and plot the behavior of sparsemax truncation in Figure \ref{fig:simplex_truncate}.
  We focus on Gaussian policies which are common for continuous-action algorithms.
% \begin{figure}
%     \centering
%     \begin{subfigure}[b]{0.49\textwidth}
%         \centering
%         \includegraphics[width=\textwidth]{img/tsallis_entropy.png}
%         \label{fig:y equals x}
%     \end{subfigure}
%     \hfill
%     \begin{subfigure}[b]{0.49\textwidth}
%         \centering
%         \includegraphics[width=\textwidth]{img/tsallis_kl.png}
%         \label{fig:three sin x}
%     \end{subfigure}
%     \caption{Estimation of policy ratio $\frac{\pi_{k+1}}{\pi_k}$ during learning of Munchausen DQN on \texttt{CartPole-v1} and \texttt{LunarLander-v2}.
%     Notice the $y$-axis is at the magnitude of $10^{35}$.
%     }
%     \label{fig:mdqn_policy_ratio}
% \end{figure}

Very recently \citet{zhu2023generalized} proposed in RL to exploit Tsallis KL divergence \citep{Furuichi2004-fundamentals-qKL} which generalizes Tsallis entropy.  
They proved that the regularized optimal policy takes a similar form to the optimal KL-regularized policy:
% Recall that, this definition is different from the statistical physics definition \citep{Furuichi2004-fundamentals-qKL}:
\begin{align}
    \begin{split}
        \qKLany{\pi(\cdot|s)}{\mu(\cdot|s)} \!=\! -\sum_a \pi(a|s) \ln_{q} \frac{\mu(a|s)}{\pi(a|s)}, \,\, \pi(a|s) = \mu(a|s) \exp_q\AdaBracket{\frac{Q_{\pi}(s,a)}{\tau} - \psi\AdaBracket{\frac{Q_{\pi}(s,a)}{\tau}} \!}.
    \end{split}
    \label{eq:tkl_policy}
\end{align}
We also write the policy as $\pi(a|s)\propto \mu(a|s)\exp_q\AdaBracket{\frac{Q_{\pi}(s,a)}{\tau}}$.
It is worth noting that unlike the KL divergence, the Tsallis KL divergence cannot be decomposed as $\ln_q\!\frac{\pi(a|s)}{\mu(a|s)} \neq \ln_q \pi(a|s) - \ln_q \mu(a|s)$.
% \eq{\ref{eq:tkl_policy}} is important to our application of offline RL where we show the in-sample softmax becomes in-sample sparsemax.

\begin{figure}
    \centering
    \begin{subfigure}[b]{0.45\textwidth}
        \includegraphics[width=\textwidth]{img/2-simplex.png}
    \end{subfigure}
    \begin{subfigure}[b]{0.4\textwidth}
        \includegraphics[width=\textwidth]{img/Gaussian_ks.png}
    \end{subfigure}
    \caption{
        (Left) Comparison between argmax, softmax and sparsemax on the probability simplex. Argmax produces a deterministic policy residing on the vertices, while a softmax policy lies inside the simplex. By contrast, a sparsemax policy lives on the border.
        (Right) Sparsemax operator acting on a Gaussian policy by truncating actions with value below the threshold $\psi$.
        Actions with value larger than $\psi$ are collected in the set $K(s)$.
    }
    \label{fig:simplex_truncate}
\end{figure}

% \begin{figure}[t]
%     \centering
%     \begin{subfigure}[b]{0.245\textwidth}
%         \includegraphics[width=\textwidth]{img/q2_Gaussian_sparsemax.png}
%     \end{subfigure}
%     \begin{subfigure}[b]{0.245\textwidth}
%         \includegraphics[width=\textwidth]{img/q50_scaled_Gaussian_sparsemax.png}
%     \end{subfigure}
%     \begin{subfigure}[b]{0.245\textwidth}
%         \includegraphics[width=\textwidth]{img/q2.0_Boltzmann_sparsemax.png}
%     \end{subfigure}
%     \begin{subfigure}[b]{0.245\textwidth}
%         \includegraphics[width=\textwidth]{img/q50_Boltzmann_sparsemax.png}
%     \end{subfigure}
%     \caption{
%         The sparsemax operator acting upon Gaussian and Boltzmann policies for $q=2$ and $q=50$ by truncating actions with values lower than $\psi$. 
%     As $q\rightarrow \infty$ the policy tends toward uniform distribution.
%     We assume the The dataset is generated by Tsallis policies such that the actions absent from the offline dataset are those being truncated.
%     }
%     \label{fig:q_truncation}
% \end{figure}

@@

More importantly, the support constraint is naturally satisfied since 
the learned Tsallis policy learns a new set of allowable actions $K_{t, q}$ from $K_\mathcal{D}(s)$ depending on $q$ and iteration $t$.
The set satisfies the condition $K_{t, q} \preceq K_\mathcal{D}$:
 i.e. $|K_{t, q}| \leq |K_\mathcal{D}|$ and support constraint $\pi_t \preceq \datasetPolicy$.
 Let us take $q=2$ for example:
 \begin{align}
    \begin{split}
    &Q_{t+1, \datasetPolicy}(s,a) = r(s,a) +  \gamma \expectation{s'\sim P(\cdot | s,a)}{ \sum_{a' \in K_{\mathcal{D}}(s)} \!\!\!\!\! \pi_{t+1}(a'|s') \AdaBracket{Q_{t, \datasetPolicy}(s',a') - \tau S_2(\pi_{t+1}(\cdot|s'))}}\\
    &\qquad = r(s,a) + \gamma \expectation{s'\sim P(\cdot | s,a)}{ \tau\sum_{a' \in K_{\mathcal{D}}(s)} \!\! \AdaBracket{\frac{Q_{t, \datasetPolicy}(s',a')}{\tau}}^2 - \AdaBracket{ \psi\AdaBracket{\frac{Q_{t, \datasetPolicy}(s',a')}{\tau}} - 1 }^2 + \tau}\\
    &\qquad = r(s,a) + \gamma \expectation{s'\sim P(\cdot | s,a)}{ \tau\sum_{a' \in K_{t,q}(s)} \!\! \AdaBracket{\frac{Q_{t, \datasetPolicy}(s',a')}{\tau}}^2 - \AdaBracket{ \psi\AdaBracket{\frac{Q_{t, \datasetPolicy}(s',a')}{\tau}} - 1 }^2 + \tau}.
    \end{split}
    \label{eq:tsallis_backward_q2}
 \end{align}
 The second equation is because $\max_{\pi}\sum_{a\in\pi(\cdot|s)}\pi(a|s)Q(s,a) + \tau S_2(\pi(\cdot|s))$ attains its maximum at $\tau \sum_{a \in K(s)}\AdaBracket{ \frac{Q(s,a)}{\tau} }^2 - \psi\AdaBracket{\frac{Q(s, \cdot)}{\tau}}^2 + \tau$ \cite{Lee2018-TsallisRAL,Martins16-sparsemax}, and the last equation is due to $K_{t, q} \preceq K_\mathcal{D}$.
 \eq{\ref{eq:tsallis_backward_q2}} states that, one needs not to explicitly enforce the support constraint since it is automatically fulfilled by learning a new subset of allowable actions.
% That is, the backward Bellman optimality equation becomes:
% \begin{align}
%     \begin{split}
%         \datasetOptimalQ(s,a) &= r(s,a) +  \gamma \expectation{s'\sim P(\cdot | s,a)}{ \sum_{a' \in K_\mathcal{D}(s')} \pi_{*, \datasetPolicy}(a'|s') \AdaBracket{\datasetOptimalQ(s',a') - \tau S_2(\pi_{*, \datasetPolicy})(\cdot|s')}}. 
%     \end{split}
% \end{align}
% The term inside the expectation is now:
% \begin{align}
%     \begin{split}
%         & \sum_{a' \in K_\mathcal{D}(s')} \pi_{*, \datasetPolicy}(a'|s') \AdaBracket{\datasetOptimalQ(s',a') - \tau S_2(\pi_{*, \datasetPolicy})(\cdot|s')} \\ 
%          &= \sum_{a' \in K_\mathcal{D}(s')} \pi_{*, \datasetPolicy}(a'|s') \AdaBracket{ \datasetOptimalQ(s',a') + \frac{\tau}{2}(1 - \pi_{*, \datasetPolicy}(a'|s')) } \\
%          &= \sum_{a' \in K_\mathcal{D}(s')} \pi_{*, \datasetPolicy}(a'|s') \AdaBracket{ \datasetOptimalQ(s',a') - \frac{\tau}{2}\pi_{*, \datasetPolicy}(a'|s') } + \frac{\tau}{2} \\
%          &= \sum_{a' \in K_\mathcal{D}(s')} \frac{\AdaRectBracket{ \tau^{-1}Q_{t, \datasetPolicy}(s,a)}_+ }{\sum_{b\in K_\mathcal{D}(s')}\tau^{-1} Q_{t, \datasetPolicy}(s,b)}
%     \end{split}
% \end{align}
